What is an Ancestral Recombination Graph?

### 2022-02-11 paper.tex
Fix error in WF sim

\end{tikzpicture}
\\
(A) & (B) \\
\end{tabular}
\caption{\label{fig-arg-data-structure}
Encoding an ARG. (A) The classical approach described by Griffiths
equates graph nodes with events in the stochastic process
associates recombination breakpoints with nodes. This encoding
is limited in the ancestral patterns that can be described and ambiguous.
(B) Equating graph nodes with \emph{genomes} and attaching the
interval of genome inherited by the child node with edges removes
this ambiguity and can describe any pattern of genetic inheritance.
\textcolor{red}{This is very much a draft; let's see how it works with
 the text and other figures and tidy it up in a later revision}
}
\end{figure}

>>>>

\end{tikzpicture}
\\
(A) & (B) \\
\end{tabular}
\caption{\label{fig-arg-data-structure}
Encoding an ARG. (A) The classical approach described by Griffiths
equates graph nodes with events in the stochastic process,
and associates recombination breakpoints with nodes. This encoding
is limited in the ancestral patterns that can be described and ambiguous.
(B) Equating graph nodes with \emph{genomes} and attaching the
interval of genome inherited by the child node with edges removes
this ambiguity and can describe any pattern of genetic inheritance.
\textcolor{red}{This is very much a draft; let's see how it works with
 the text and other figures and tidy it up in a later revision}
}
\end{figure}
